Scheeper's Meager-NWD Game and the Menger Game

### 2014-12-03 phd/dissertation/chapter5.tex
finish rewrite of main ch 5 proof

\begin{lem}
  If $\pl K\ktactwin{k+2}\gruKPGame{\pmb X}$, then
  $\pl K\ktactwin{k+1}\gruKPGame{\pmb X}$.
\end{lem}

\begin{proof}
  \newcommand{\hi}{\text{height}}
  \newcommand{\de}{\text{depth}}
  Fix an arbitrary $y\in X$. For $\pmb t\in \pmb X^{<\omega}$, define the
  following:
    \begin{itemize}
      \item $\hi(\pmb t)<\omega$ satisfying
            $|s|\leq \hi(\pmb t)$ for each
            $\<x,s\>\in(X\times 2^{<\omega})\cap \ran{\pmb t}$
      \item $\de(\pmb t)\in [X]^{<\omega}$ satisfying
            $x\in\de(\pmb t)$ for each
            $\<x,s\>\in(X\times 2^{<\omega})\cap \ran{\pmb t}$
      % \item $\pmb R(\pmb t)\in [\pmb X^{<\omega}]^{<\omega}$ such that
      %       $\pmb r\in \pmb R(\pmb t)$
      %       satisfies one of the following:
      %   \begin{itemize}
      %     \item $\pmb r(i)=c$ where $c\in C\cap\ran{\pmb t}$
      %     \item $\pmb r(i)=\<x,s\>$ where $s\leq\hi(\pmb t)$,
      %                                     $x\in\de(\pmb t)$
      %     \item $\pmb r(i)=\<y,s\>$ where $s\leq\hi(\pmb t)$
      %   \end{itemize}
    \end{itemize}

  For each compact set $C$, define $F(C)\in[\omega_1]^{<\omega}$ and
  $m(C)<\omega$ such that $C\subseteq K'_{F(C)}\cup L_{m(C)}$.

  Let $\sigma$ be a winning $k+2$-tactic for $\pl K$.
  For $\pmb t\in \pmb X^{<\omega}$, let $\pmb r\preceq \pmb t$ denote that
  $\pmb r$ is a subsequence of a permutation of $\pmb t$, and let
  $\pmb r\preceq_i \pmb t$ denote that $\pmb r$ is a subsequence of a
  permutation of $\pmb t\concat\<\<y,s\>\>$ for some $s\in 2^{\leq i}$.

  Let $M(\pmb t)=\max_{\pmb r\preceq \pmb t} m(\sigma(\pmb r\rest^{k+2}))$.
  We construct a $k+1$-tactic $\tau$ for $\pl K$ as follows:
    \[
      \tau(\pmb t)
        =
      \bigcup_{\pmb r\preceq_{|M(\pmb t)|} \pmb t}
      \sigma(\pmb r)
    \]
  Let $\pmb p:\omega\to\pmb X$ be a legal attack against $\tau$, so
    \[
      \pmb p(n)
        \not\in
      \bigcup_{m\leq n}
      \tau(\pmb p\rest^{k+1} m)
    \]
  Define the attack $\pmb q:\omega\to\pmb X$ as follows for $i<\omega$,
  $j<k+1$:
    \[
      \pmb q((k+2)i+j) = \pmb p((k+1)i+j)
    \]
    \[
      \pmb q((k+2)i+(k+1)) = \<y,a_{|M()|}\>
    \]

\end{proof}

>>>>

\begin{lem}
  If $\pl K\ktactwin{k+1}\gruKPGame{\pmb X}$, then
  $\pl K\tactwin\gruKPGame{\pmb X}$.
\end{lem}

\begin{proof}
  Let $\sigma$ be a winning $(k+1)$-tactical strategy, and without loss of
  generality assume it ignores order.

  Define $F(x_0,\dots,x_{k},n)\in [C]^{<\omega}$ and
  $m(x_0,\dots,x_{k},n)\in\omega\setminus(n+1)$, both increasing on $n$,
  such that for each $\<x_0,\dots,x_{k}\>\in X^{k+1}$,
  \[
    \bigcup_{s_0,\dots,s_k \in 2^{\leq n}}
    \sigma(\<x_0,s_0\>,\dots,\<x_{k},s_{k}\>)
      \subseteq
    K'_{F(x_0,\dots,x_{k},n)} \cup L_{m(x_0,\dots,x_{k},n)}
  \]

  Select an arbitrary point $y \in X$.
  Let
    \[
      M^0(x,n)=n
    \]
    \[
      M^{i+1}(x,n)=m(x,y,\dots,y,M^i(x,n)+1)
    \]
  and define the tactical strategy $\tau$ as follows:
  \[
    \tau(\emptyset)
      =
    \sigma(\emptyset)
  \]
  \[
    \tau(\<c_\alpha\>)
      =
    \{c_\alpha\}
  \]
  \[
    \tau(\<\<x,s\>\>)
      =
    K'_{F(x,y,\dots,y,M^k(x,|s|)+1)}
      \cup
    L_{m(x,y,\dots,y,M^k(x,|s|)+1)}
  \]

  Let $\pmb p:\omega\to \pmb X$ be a legal attack against
  $\tau$, and assume $\pmb p(n)=\<x_n,s_n\>\in X\times 2^{<\omega}$.
  Then consider the attack $\pmb q:\omega\to X\times 2^{<\omega}$ against
  $\sigma$ defined by, for $n<\omega$ and $i<k$,
    \[
      \pmb q((k+1)n)=\pmb p(n)=\<x_n,s_n\>
    \]
    \[
      \pmb q((k+1)n+(i+1))=\<y, a_{M^{i+1}(x_n,|s_n|)}\>
    \]

  Since
    \[
      \<x_{n+1},s_{n+1}\>
        =
      \pmb p(n+1)
        \not\in
      \tau(\<\pmb p(n)\>)
        \supseteq
      L_{M^{k+1}(x_n,|s_n|)+1}
    \]
  it follows that
  $|s_{n+1}|\geq M^{i+1}(x_n,|s_n|)+1$ for $i<k$; furthermore,
    \[
      |s_n|
        \leq
      M^i(x_n,|s_n|)
        <
      M^i(x_n,|s_n|)+1
        \leq
      M^{i+1}(x_n,|s_n|)
        <
      M^{i+1}(x_n,|s_n|)+1
        \leq
      |s_{n+1}|
    \]
  so the second coordinate of $\pmb q(n)$ is always strictly increasing.

  By the definition of $\tau$,
    \[
      \pmb q((k+1)n)
        =
      \pmb p(n)
        \not\in
      \bigcup_{m\leq n}
      \tau(\pmb p\rest^1 m)
        \supseteq
      \bigcup_{m\leq (k+1)n}
      \sigma(\pmb q\rest^{k+1} m)
    \]

  Since
    \[
      \pmb q((k+1)n+(i+1))
        =
      \<y, a_{M^{i+1}(x_n,|s_n|)}\>
        \in
      X\times A
    \]
  it follows that $\pmb q((k+1)n+(i+1))\not\in K'_F$ for any
  $F\in[\omega_1]^{<\omega}$.

  Then it's sufficient to note that
    \[
      |a_{M^{i+1}(x_n,|s_n|)}|
        =
      M^{i+1}(x_n,|s_n|) + 1
        >
      m(x_n,y,\dots,y,M^i(x_n,|s_n|)+1)
    \]
  to show that
    \[
      \pmb q((k+1)n+(i+1))
        =
      \<y, a_{M^{i+1}(x_n,|s_n|)}\>
        \not\in
      L_{m(x_n,y,\dots,y,M^i(x_n,|s_n|)+1)}
    \]
  and therefore $\pmb q((k+1)n+(i+1))$ is a legal move.

  As a result, $\pmb q$ is a legal attack against $\sigma$, and
  $\{\{\pmb q(n)\}:n<\omega\}\supseteq\{\{\pmb p(n)\}:n<\omega\}$ are
  both locally finite.

  Finally, if the range of $\pmb p$ intersects $C$, those moves may be safely
  ignored as they cannot be repeated and lay in a closed discrete set,
  so the proof is complete.
\end{proof}
